### 2021-08-29 manuscript/methodology.tex
Correcoes nop pseudo algoritmo cgls.
until subsection "Standard CGLS method"

%======================================================================================
\subsection*{The total-field anomaly}
%======================================================================================

The Earth's magnetic field is commonly divided in three parts: main field, crustal field and external field. The main field is generated in the outter core in a process of self-sustaining dynamo, the crustal field is generated by magnetic bodies in the litosphere and the external field is generated by electrical currents in the ionosphere and magnetosphere. For exploration geophysics, the crustal field is the object of study, which makes the separation of this data from the acquisition dataset a very important step.

The combination of the main field and crustal field is known as internal field or total-field. Taking the difference between this internal field and the main field given by a model (e.g. IGRF), at the same location, we have the total-field anomaly.

Let $(x_i, y_i, z_i), i =  1,2,3,...N$, be a observed dataset in a region considering a right-handed Cartesian coordinate system with the $x$-axis pointing north, $y$-axis pointing east and $z$-axis pointing downward. The total-field anomaly at the $i$th observation can be approximated to:
\begin{equation}
	\Delta T(x_i, y_i, z_i) = \hat{\mathbf{F}}^{\top} \mathbf{B}(x_i, y_i, z_i) \: ,
	\label{eq:tfanomaly}
\end{equation}
where, $\mathbf{B}(x_i, y_i, z_i)$ is the crustal field, $\hat{\mathbf{F}}^{\top}$ is the transposed unitary vector with the main field directions, with $\hat{\mathbf{F}}$ described as:
\begin{equation}
	\hat{\mathbf{F}} = \left[
	\begin{array}{c}
		F_x \\
		F_y \\
		F_z
	\end{array} \right] = 
	\left[
	\begin{array}{c}
		\cos(I_{0}) \, \cos(D_{0}) \\
		\cos(I_{0}) \, \sin(D_{0}) \\
		\sin(I_{0})
	\end{array} \right],
	\label{eq:unit_vector_F}
\end{equation}
where $I_{0}$ is the inclination and $D_{0}$ the declination of the main field, respectively.

Considering a uniform magnetized body with volume $v$ and a total magnetization vector $\mathbf{m}$, the induced magnetic field is:
\begin{equation}
	\mathbf{B}(x_i, y_i, z_i) = c_{m} \, \frac{\mu_{0}}{4\pi} \: \mathbf{M}(x_i, y_i, z_i) \: 
	\mathbf{m} \: ,
	\label{eq:induction-general}
\end{equation}
where, $\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, 
$c_{m} = 10^{9}$ is a constant that transforms the induced magnetic field from Tesla (T) to nanotesla (nT) and 
$\mathbf{M}(x_i, y_i, z_i)$ is a $3 \times 3$ matrix given by:
\begin{equation}
	\mathbf{M}(x_i, y_i, z_i) =
	\left[
	\begin{array}{ccc}
		\partial_{xx} \phi(x_i,y_i,z_i) & \partial_{xy} \phi(x_i,y_i,z_i) & 
		\partial_{xz} \phi(x_i,y_i,z_i) \\
		\partial_{xy} \phi(x_i,y_i,z_i) & \partial_{yy} \phi(x_i,y_i,z_i) & 
		\partial_{yz} \phi(x_i,y_i,z_i) \\
		\partial_{xz} \phi(x_i,y_i,z_i) & \partial_{yz} \phi(x_i,y_i,z_i) & 
		\partial_{zz} \phi(x_i,y_i,z_i)
	\end{array}
	\right] \: ,
	\label{eq:M}
\end{equation}
where, $\partial_{\alpha\beta} \phi(x_i,y_i,z_i)$ with $\alpha = x, y, z$ and 
$\beta = x, y, z$, are the second derivatives of the function $\phi(x_i,y_i,z_i)$
with respect to $x$, $y$ and $z$:

\begin{equation}
	\phi(x_i,y_i,z_i) = \int\int\limits_{v}\int \frac{1}{r} \: dv,
	\label{eq:phi}
\end{equation}
where the function $\dfrac{1}{r}$ is given by:

\begin{equation}
	\dfrac{1}{\sqrt{(x_i - x_j)^{2} + 
			(y_i - y_j)^{2} + (z_i - z_j)^{2}}} \,
	\label{eq:r}
\end{equation}
and $x_j, y_j, z_j$ are the $j$th Cartesian coordinates within the volume elements of the magnetized body with volume $v$, where the integral (equation \ref{eq:phi}) is conducted.

Rewriting the equation \ref{eq:tfanomaly} using the magnetic induction given by equation \ref{eq:induction-general} the total-field anomaly $\Delta T(x, y, z)$ is given by:
\begin{equation}
\Delta T(x_i, y_i, z_i) = c_{m} \, \frac{\mu_{0}}{4\pi} \, m \: \hat{\mathbf{F}}^{\top} 
\mathbf{M}(x_i, y_i, z_i) \: \hat{\mathbf{m}} \: ,
\label{eq:tfanomaly-general}
\end{equation}
where $m$ is the magnetization intensity and $\hat{\mathbf{m}}$ is the directional unitary vector.

%======================================================================================
\subsection*{Equivalent layer for magnetic data}
%======================================================================================

Grounded on the equivalent layer principle it is possible to calculate the total-field anomaly $\Delta T(x_i, y_i, z_i)$ (equation \ref{eq:tfanomaly-general}) with the convolution between the harmonic function and the physical property:
\begin{equation}
\Delta T(x_{i}, y_{i}, z_{i})
= \int \limits_{-\infty}^{+\infty}
\int \limits_{-\infty}^{+\infty}
p(x_j, y_j, z_{c}) \,
\left[ c_{m} \, \frac{\mu_{0}}{4\pi} \,
\hat{\mathbf{F}}^{\top} \mathbf{H} \, 
\hat{\mathbf{h}} \right] \,
dx \, dy \: ,
\label{eq:tf-p-continuous-mag-positive}
\end{equation}
where $z_c$ is a constant representing the depth of the equivalent layer with $z_i < z_c$. The unitary vector $\hat{\mathbf{h}}$ is the magnetization directions of the equivalent sources over the layer:
\begin{equation}
\hat{\mathbf{h}} = \left[
\begin{array}{c}
{h}_x \\
{h}_y \\
{h}_z
\end{array} \right] = 
 \left[
\begin{array}{c}
\cos(I) \, \cos(D) \\
\cos(I) \, \sin(D) \\
\sin(I)
\end{array}
\right] \: ,
\label{eq:h_hat}
\end{equation}
where $I$ and $D$ are, respectively, the inclination and declination of the equivalent sources, $\mathbf{H}$ is a $3 \times 3$ matrix that contains the second derivatives in relation to the observed Cartesian coordinates $x, y, z$ as presented in equation \ref{eq:r}:
\begin{equation}
\mathbf{H} =
\left[
\begin{array}{ccc}
\partial_{xx} \frac{1}{r} & 
\partial_{xy} \frac{1}{r} & 
\partial_{xz} \frac{1}{r} \\
\partial_{xy} \frac{1}{r} & 
\partial_{yy} \frac{1}{r} & 
\partial_{yz} \frac{1}{r} \\
\partial_{xz} \frac{1}{r} & 
\partial_{yz} \frac{1}{r} & 
\partial_{zz} \frac{1}{r}
\end{array}
\right] \: =
\left[
\begin{array}{ccc}
H_{xx} & 
H_{xy} & 
H_{xz} \\
H_{xy} & 
H_{yy} & 
H_{yz} \\
H_{xz} & 
H_{yz} & 
H_{zz}
\end{array}
\right] \: ,
\label{eq:Hi}
\end{equation}
and the physical property $p(x_j, y_j, z_{c})$ represents the magnetic dipole moment distribution over the layer and has unit of $Am^2$.

Discretizing equation \ref{eq:tf-p-continuous-mag-positive} we get:
\begin{equation}
\Delta T(x_{i}, y_{i}, z_{i}) = \sum_{j=1}^{M} p_j a_{ij}\: ,
\label{eq:integral-sum_mag}
\end{equation}
where $j = 1,2,3,...,M$ are the equivalent sources discretized and distributed across the layer and $a_{ij}$ is given by:
\begin{equation}
a_{ij}
= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: .
\label{eq:aij_mag}
\end{equation}
Equation \ref{eq:integral-sum_mag} can be written as:
\begin{equation}
\mathbf{d}(\mathbf{p}) = \mathbf{A} \mathbf{p} \: ,
\label{eq:predicted-data-vector_mag}
\end{equation}
where $\mathbf{d}(\mathbf{p})$ is the vector of total-field anomaly, $\mathbf{A}$ is a matrix containing the elements given by equation \ref{eq:aij_mag}, also known as the sensitivity matrix and $\mathbf{p}$ is the vector containing the dipole moments of each equivalent source. By using the normal equations:
\begin{equation}
	\mathbf{A}^{\top}\mathbf{A}{\mathbf{p}} = 
	\mathbf{A}^{\top} \mathbf{d}^{o} \:
	\label{eq:normal-equations}
\end{equation} 
which is a conventional manner of solving linear systems, the estimative of the dipole moment parameters vector can be calculated from the total-field anomaly as:
\begin{equation}
\hat{\mathbf{p}} = \left( \mathbf{A}^{\top}\mathbf{A} %+ 
%\mu \, \mathbf{I} 
\right)^{-1}
\mathbf{A}^{\top} \mathbf{d}^{o} \:
\label{eq:estimated-p-parameter-space}
\end{equation}
where $\mathbf{d}^{o}$ is the observed total-field anomaly. Equation \ref{eq:estimated-p-parameter-space} will be referenced throughout this work as the classical method for solving the equivalent layer.

%======================================================================================
\subsection{Conjugate Gradient Least Square method (CGLS)}
%======================================================================================

As an alternative from the clasical method of parameter estimative, the conjugate gradient (CG) is a well-known iterative method for solving linear systems with symmetric positive definite matrices. By minimizing the quadratic form:
\begin{equation}
\, \Phi(\mathbf{p}) = \frac{1}{2} \, \mathbf{p}^{\top} \, \mathbf{A} \, \mathbf{p} \,
- \mathbf{{d}^{o}}^{\top} \, \mathbf{p}\: ,
\label{eq:estimated-p-cg}
\end{equation}
it is possible to solve the system by constructing a basis of conjugate directions $c \in R^N$ \citep{aster2018parameter}. As we are solving a general least square problem and matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is not symmetric, instead we minimize:
\begin{equation}
\, || \mathbf{A} \, \mathbf{p} - \mathbf{d}^o||_2 \: ,
\label{eq:estimated-p-cgls}
\end{equation}
by applying the conjugate gradient to the normal equations (equation \ref{eq:normal-equations}).

In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.

A pseudocode for the CGLS method follows:

\begin{algorithm}[H]
	Input: $\mathbf{A} \in R^{N \times M} $ and $\mathbf{d}^o \in R^N$.

	Output: Estimative of parameter vector $\hat{\mathbf{p}}$.

	Let $it = 0$, $\hat{\mathbf{p}}^{(0)} = {\mathbf{0}}$, $\mathbf{c}^{(-1)} = {\mathbf{0}}$, $\beta_0 = 0$, $\mathbf{s}^{(0)} = \mathbf{d}^{o} - \mathbf{A} \hat{\mathbf{p}}^{(0)}$ and $\mathbf{r}^{(0)} = \mathbf{A}^{\top} \mathbf{s}^{(0)}$.

	1 - If $it > 0$, let $\beta_{(it)} = \dfrac{{\mathbf{r}^{(it)}}^{\top} \, \mathbf{r}^{(it)}} {{\mathbf{r}^{(it - 1)}}^{\top} \, \mathbf{r}^{(it - 1)}}$

	2 - $\mathbf{c}^{(it)} = \mathbf{r}^{(it)} - \alpha_{(it)} \,\beta_{(it)} \, \mathbf{c}^{(it - 1)}$.

	3 - $\alpha_{(it)} = \dfrac{{||\mathbf{r}^{(it)}||^2_2}}{({\mathbf{c}^{(it)}}^{\top} \, \mathbf{A}^{\top})(\mathbf{A} \, \mathbf{c}^{(it)})}$.

	4 - $\hat{\mathbf{p}}^{(it + 1)} = \hat{\mathbf{p}}^{(it)} - \alpha_{(it)} \, \mathbf{c}^{(it)}$.

	5 - $\mathbf{s}^{(it + 1)} = \mathbf{s}^{(it)} - \alpha_{(it)} \, \mathbf{A} \, \mathbf{c}^{(it)}$.

	6 - $\mathbf{r}^{(it + 1)} = \mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$.

	7 - $it = it + 1$.

@@

	\caption{Conjugate Gradient Least Square pseudocode \citep[][ p. 166]{aster2018parameter}.}
\label{al:cgls-algorithm}
\end{algorithm}

Different from the classical least-square solution (equation \ref{eq:estimated-p-parameter-space}), the CGLS solution (Algorithm 1) requires neither inverse matrix nor matrix-matrix product.The CGLS method only requires: one matrix-vector multiplication out of the loop and two matrix-vector multiplications, in steps 3 and 6, at each iteration.

In this work, we will reduce the computational cost of the equivalent layer by substituting exactly these two matrix-vector products with a much more efficient algorithm.

@@

As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.

@@

To compare the efficiency of our algorithm we will use a numerical approach and calculate the floating-point operations (\emph{flops}), i.e., count the number of mathematical operations necessary to complete the estimative of parameter vector $\mathbf{\hat{p}}$ of the normal equations (equation \ref{eq:estimated-p-parameter-space}) and both the CGLS methods (algorithm \ref{al:cgls-algorithm}) for calculating the matrix-vector product by its standart way and our approach.

>>>>

%======================================================================================
\subsection{Classical equivalent layer for magnetic data}
%======================================================================================

Let $\mathbf{d}^{o}$ be the $N \times 1$ observed data vector, whose $i$th element 
is the total-field anomaly $d^{o}_{i}$ produced by arbitrarily magnetized sources
at the position $(x_{i}, y_{i}, z_{i})$, $i =  1, \dots, N $, 
of a right-handed Cartesian coordinate system with $x$-, $y$- and $z$-axis 
pointing to north, east and down, respectively.
We consider that the total-field anomaly data $d^{o}_{i}$ represent the discrete
values of a harmonic function. Besides, we consider that the main geomagnetic field 
direction at the study area can be defined by the unit vector
\begin{equation}
\hat{\mathbf{F}} = \begin{bmatrix}
F_x \\
F_y \\
F_z
\end{bmatrix} =
\begin{bmatrix}
\cos(I_{0}) \, \cos(D_{0}) \\
\cos(I_{0}) \, \sin(D_{0}) \\
\sin(I_{0})
\end{bmatrix} \: ,
\label{eq:unit_vector_F}
\end{equation}
with constant inclination $I_{0}$ and declination $D_{0}$.
In this case, $d^{o}_{i}$ can be approximated by the predicted total-field anomaly
\begin{equation}
\Delta T_{i} = \sum_{j=1}^{M} \, p_{j} a_{ij} \: ,
\label{eq:integral-sum_mag}
\end{equation}
which describes the magnetic induction exerted, at the observation point $(x_{i}, y_{i}, z_{i})$,
by a discrete layer of $M$ dipoles (equivalent sources) defined on the horizontal plane $z = z_{c}$, 
where $p_{j}$ is the magnetic moment intensity (in A~m~$^{2}$)~of the $j$th dipole, 
that has unit volume and is located at the point $(x_{j}, y_{j}, z_{c})$. In equation
\ref{eq:integral-sum_mag}, $a_{ij}$ is the harmonic function
\begin{equation}
a_{ij}
= c_{m} \, \frac{\mu_{0}}{4\pi} \, \hat{\mathbf{F}}^{\top} \mathbf{H}_{ij} \: \hat{\mathbf{h}} \: ,
\label{eq:aij_mag}
\end{equation}
the unit vector
\begin{equation}
\hat{\mathbf{h}} = \begin{bmatrix}
h_x \\
h_y \\
h_z
\end{bmatrix} =
\begin{bmatrix}
\cos(I) \, \cos(D) \\
\cos(I) \, \sin(D) \\
\sin(I)
\end{bmatrix} \: ,
\label{eq:h_hat}
\end{equation}
defines the magnetization direction of all dipoles, with constant inclination $I$ and declination $D$,
$\mu_{0} = 4\pi \, 10^{-7}$ H/m is the magnetic constant, $c_{m} = 10^{9}$ is a factor that transforms
the magnetic induction from Tesla (T) to nanotesla (nT) and $\mathbf{H}_{ij}$ is a $3 \times 3$ matrix 
\begin{equation}
\mathbf{H}_{ij} = \begin{bmatrix}
\partial_{xx} \frac{1}{r_{ij}} & 
\partial_{xy} \frac{1}{r_{ij}} & 
\partial_{xz} \frac{1}{r_{ij}} \\
\partial_{xy} \frac{1}{r_{ij}} & 
\partial_{yy} \frac{1}{r_{ij}} & 
\partial_{yz} \frac{1}{r_{ij}} \\
\partial_{xz} \frac{1}{r_{ij}} & 
\partial_{yz} \frac{1}{r_{ij}} & 
\partial_{zz} \frac{1}{r_{ij}}
\end{bmatrix} \: ,
\label{eq:Hij}
\end{equation}
where $\partial_{\alpha\beta} \frac{1}{r_{ij}}$, $\alpha = x, y, z$, $\beta = x, y, z$, 
represent the second derivatives of the inverse distance function
\begin{equation}
\frac{1}{r_{ij}} = 
\frac{1}{\sqrt{\left(x_{i} - x_{j} \right)^{2} + 
\left(y_{i} - y_{j} \right)^{2} + \left(z_{i} - z_{c} \right)^{2}}}
\label{eq:1_rij}
\end{equation}
with respect to the coordinates of the observation point $(x_{i}, y_{i}, z_{i})$.

Equation \ref{eq:integral-sum_mag} can be rewritten in matrix notation as follows:
\begin{equation}
\mathbf{d}(\mathbf{p}) = \mathbf{A} \mathbf{p} \: ,
\label{eq:predicted-data-vector_mag}
\end{equation}
where $\mathbf{d}(\mathbf{p})$ is the $N \times 1$ predicted data vector with $i$th element defined
be the predicted total-field anomaly $\Delta T_{i}$ (equation \ref{eq:integral-sum_mag}),
$\mathbf{p}$ is the $M \times 1$ parameter vector whose $j$th element is the magnetic moment intensity
$p_{j}$ of the $j$th dipole and $\mathbf{A}$ is the $N \times M$ sensitivity matrix with element 
$ij$ defined by the harmonic function $a_{ij}$ (equation \ref{eq:aij_mag}).
In the classical equivalent-layer technique, the common approach for 
estimating the parameter vector $\mathbf{p}$ from the observed 
total-field anomaly data $\mathbf{d}^{o}$ is solving the least-squares normal equations
\begin{equation}
\mathbf{A}^{\top}\mathbf{A} \: \mathbf{p} = 
\mathbf{A}^{\top} \mathbf{d}^{o} \: .
\label{eq:normal-equations}
\end{equation}
This equation is usually solved by first computing the Cholesky factor of matrix
$\mathbf{A}^{\top}\mathbf{A}$ and then using it to solve the linear system
\citep[][ p. 262]{golub-vanloan2013}. 
The estimated parameter vector obtained by following this approach will be 
referenced throughout this work as the \textit{classical solution}.

%======================================================================================
\subsection{Standard Conjugate Gradient Least Squares (CGLS) method}
%======================================================================================

The computational cost associated with the classical method for estimating the parameter 
vector $\mathbf{p}$ by solving the linear system \ref{eq:normal-equations} can be very high 
or ever prohibitive when dealing with large data sets. In these cases, a well-known alternative
is solving the normal equations (equation \ref{eq:normal-equations}) iteratively by 
using the standard Conjugate Gradient Least Squares (CGLS) method. Below we present a pseudocode 
for the standard CGLS method:

\begin{algorithm}[H]
	Input: $\mathbf{A}$ and $\mathbf{d}^{o}$.

	Output: Estimated parameter vector $\tilde{\mathbf{p}}$.

	Set $it = 0$, $\tilde{\mathbf{p}}_{(it)} = \mathbf{0}$, $\mathbf{c}_{(it-1)} = \mathbf{0}$, $\beta_{(it)} = 0$, $\mathbf{s}_{(it)} = \mathbf{d}^{o}$ and $\mathbf{r}_{(it)} = \mathbf{A}^{\top} \mathbf{s}_{(it)}$.

	1 - If $it > 0$, $\beta_{(it)} = \dfrac{\| \mathbf{r}_{(it)} \|_{2}^{2}}{\| \mathbf{r}_{(it - 1)} \|_{2}^{2}}$

	2 - $\mathbf{c}_{(it)} = \mathbf{r}_{(it)} - \beta_{(it)} \, \mathbf{c}_{(it - 1)}$

	3 - $\alpha_{(it)} = \dfrac{{\| \mathbf{r}_{(it)}\|_{2}^{2}}}{\| \mathbf{A} \, \mathbf{c}_{(it)} \|_{2}^{2}}$

	4 - $\tilde{\mathbf{p}}_{(it + 1)} = \tilde{\mathbf{p}}_{(it)} + \alpha_{(it)} \, \mathbf{c}_{(it)}$

	5 - $\mathbf{s}_{(it + 1)} = \mathbf{s}_{(it)} - \alpha_{(it)} \, \mathbf{A} \, \mathbf{c}_{(it)}$

	6 - $\mathbf{r}_{(it + 1)} = \mathbf{A}^{\top} \, \mathbf{s}_{(it + 1)}$

	7 - $it = it + 1$

@@

	\caption{Standard CGLS pseudocode \citep[][ p. 166]{aster2019parameter}.}
\label{al:std-cgls-algorithm}
\end{algorithm}

Setting a convergence criteria based on the minimum tolerance of the residuals is a good 
option to carry out this algorithm efficiently and still obtaining very good results. 
Another possibility is to set an invariance to the Euclidean norm of residuals between 
iterations, which would increase algorithm runtime, but with smaller residuals. 
We chose the first option, as we achieve satisfactory results. 
The estimated parameter vector obtained by using the standard CGLS method 
(Algorithm \ref{al:std-cgls-algorithm}) will be referenced throughout this work as 
the \textit{standard CGLS solution}.

Note that the standard CGLS solution (Algorithm \ref{al:std-cgls-algorithm}) requires 
neither inverse matrix nor matrix-matrix product. Instead, it only requires: one matrix-vector 
product out of the loop and two matrix-vector products per iteration (in steps 3 and 6). 
In the following subsections, we will show how to compute these three matrix-vector products 
efficiently by exploring the structure of the sensitivity matrix $\mathbf{A}$.

PAREI AQUI

@@

As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:std-cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.

@@

To compare the efficiency of our algorithm we will use a numerical approach and calculate the floating-point operations (\emph{flops}), i.e., count the number of mathematical operations necessary to complete the estimative of parameter vector $\mathbf{\hat{p}}$ of the normal equations (equation \ref{eq:estimated-p-parameter-space}) and both the CGLS methods (algorithm \ref{al:std-cgls-algorithm}) for calculating the matrix-vector product by its standart way and our approach.
